How unprecedented was the February 2021 Texas cold snap?

### 2021-05-06 doc/submission_02.tex
update caption of supplemental fig s8 following discussion w/ Edgar Virguez

DJF was supported by a gift from Gates Ventures LLC to the Carnegie Institution for Science.
The authors thank
Daniel Cohan,
Sylvia Dee,
Elisabeth Gawthrop,
Pedram Hassanzadeh,
Fred Heutte,
Adam Massmann,
Alison Silverstein,
and
Vivek Srikrishnan
for discussion of this work.
The authors also thank the developers and maintainers of the open source packages we used, in particular the pydata and pangeo communities, and the many journalists and academics whose timely reporting and commentary has informed our thinking.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{EGOVA.pdf}
  \caption{
    ERCOT generator outages from 12:00AM on 14 February 2021 to 12:00AM on 18 February 2021.
    Map produced using ERCOT's Generator Outage/Derate Visualization App (EGOVA) available at \url{https://bit.ly/EGOVA}.
    Dots show the capacity reduction compared to the full rated capacity.
    However, as discussed in ref.~\cite{ercotpublic_outagesv2:2021}, ERCOT's seasonal assessment of resource adequacy does not assume that all generators will provide 100\% of their rated capacity.
    This is particularly true of intermittent resources, so this metric will tend to over-state the generator outages associated with wind and solar resources.
    We retain this figure only to show that outages occurred across the state.
  }\label{fig:egova}
\end{figure}

>>>>

DJF was supported by a gift from Gates Ventures LLC to the Carnegie Institution for Science.
The authors thank
Daniel Cohan,
Sylvia Dee,
Elisabeth Gawthrop,
Pedram Hassanzadeh,
Fred Heutte,
Adam Massmann,
Alison Silverstein,
Vivek Srikrishnan,
and
Edgar Virgüez
for discussion of this work.
The authors also thank the developers and maintainers of the open source packages we used, in particular the pydata and pangeo communities, and the many journalists and academics whose timely reporting and commentary has informed our thinking.

@@

\begin{figure}
  \includegraphics[width=\textwidth]{EGOVA.pdf}
  \caption{
    ERCOT generator outages from 12:00AM on 14 February 2021 to 12:00AM on 18 February 2021.
    Map produced using ERCOT's Generator Outage/Derate Visualization App (EGOVA) available at \url{https://bit.ly/EGOVA}.
    Dot sizes describe the capacity reduction for each outage or derate event, which may not be the same as the difference between the power produced and what ERCOT anticipated, particularly for intermittent resources \cite{ercotpublic_outagesv2:2021}.
  }\label{fig:egova}
\end{figure}
